---
title: "Steak Preferences in the U.S."
author: 'Author: Ryan Jerving'
date: "`r format(Sys.Date(), '%A, %B %d, %Y')`"
output:
  html_document: default
  pdf_document: default
subtitle: Summary Report for the _**Mountain**_ Region
---

```{r setup, include=FALSE}

# define knitr options for this project's environment

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(messages = FALSE)

# print blanks spaces rather than NAs for missing data in tables

options(knitr.kable.NA = ' ')

# load the R packages we'll need

library(fivethirtyeight)
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggthemes)

# load steak_survey dataset from fivethirtyeight package...

data("steak_survey", package="fivethirtyeight")

# and create a subset filtering out NAs and filtered on region

sdat <- na.omit(steak_survey) %>%
  filter(region=="Mountain")

```

## Background

In May 2014, Walt Hickey at
[538.com](http://fivethirtyeight.com/) published an
article titled
["How Americans Like Their Steak."](https://fivethirtyeight.com/features/how-americans-like-their-steak/) In this article, he utilized survey data collected from 550 people which asked questions related to various risky activities, such as whether they speed in traffic, if they smoke, if they skydive, and if they prefer a riskier-than-average lottery. 

The survey also asked if they eat steak and, if so, how they prefer it to be cooked.

## Purpose

The "steak survey" dataset that was used for the ["How
Americans Like Their Steak"](https://fivethirtyeight.com/features/how-americans-like-their-steak/) article is available through the R package [`fivethirtyeight`](https://cran.r-project.org/web/packages/fivethirtyeight/index.html).

Using this dataset, this article summarizes the steak preferences for the _**Mountain**_ Region of the United States by gender.

For our summary presented here, a subset of the original steak survey was extracted to only include responses with no missing data and only included respondents from the _**Mountain**_ region of the U.S. The data subset used for our summary had `r nrow(sdat)` respondents.


## Demographic Summary Tables

The age categories of the `r nrow(sdat)` survey
respondents were:

```{r}
# create table of the age categories
tb <- sdat %>%
  select(age) %>%
  table() %>%
  prop.table()*100

# convert table to data frame
dt <- as.data.frame(tb)

# use kable from knitr package to make table
# and use kable styling from kableExtra package
knitr::kable(dt, format="html",
             col.names=c("Ages","%"),
             digits=2,
             caption="Ages of Survey Respondents") %>%
  kableExtra::kable_styling(bootstrap_options ="striped",
                            full_width=FALSE)
```

